---
title: "Homework 7"
author: "T.J. Seislove"
date: "3/3/2026"
output:
  html_document:
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
library(knitr)
```

# Diamond Prices

```{r}
data(diamonds)
```

### Filtering Data

```{r}
diamond_clean <- diamonds %>% 
  filter(color %in% c('D', 'G', 'J') & clarity %in% c('I1', 'VS1', 'IF'))

diamond_clean %>% 
  count(color, clarity) %>% 
  kable()
```

^[Problem 1 Complete]

### Scatterplots

##### Base

```{r}
ggplot(diamond_clean, aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

The relationship between diamond weight (carat) and price is definitely positive, but it doesn't look linear.

^[Problem 2 Complete]

##### Color

```{r}
ggplot(diamond_clean, aes(x = carat, y = price, color = color)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

All three color groups show a positive relationship between weight and price. The best color (D) has the steepest increase in price, and the worst color (j) has the shallowest price increase.

^[Problem 3 Complete]

##### Clarity

```{r}
ggplot(diamond_clean, aes(x = carat, y = price, color = color)) +
  geom_point(aes(shape = clarity), alpha = 0.5) +
  geom_smooth(aes(linetype = clarity), method = "lm")
```

The incorporation of diamond clarity provides a lot more information in the plot. In my opinion, there's so much going on that the plot becomes difficult to read. There are so many lines that it's a little overwhelming.

^[Problem 4 Complete]

##### Color and Clarity

```{r}
ggplot(diamond_clean, aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") +
  facet_grid(color ~ clarity)
```

It's much easier to read the plots with the groups separated. The color-clarity combination with the steepest relationship is D(best) and IF(best).

^[Problem 5 Complete]